Cleaning the data

### 2017-12-10 Analysis/data_cleaning.Rmd
Updated cleaning data

## Clean the matchings
disparity <- gsub("ss", "s", gsub("ss", "s", disparity))
disparity <- gsub(" and ", " \\+ ", disparity)
disparity <- gsub("DTT pair_distances", "pair_distances", disparity)
disparity <- gsub("DTT pair_distances", "pair_distances", disparity)
disparity <- gsub("range variance", "range \\+ variance", disparity)
disparity <- gsub("distances from centre", "centroids", disparity)
disparity <- gsub("distances from centroids", "centroids", disparity)
disparity <- gsub("distances to centroids", "centroids", disparity)
disparity <- gsub("mean ", "", disparity)
disparity <- gsub("median ", "", disparity)
disparity <- gsub("average ", "", disparity)
disparity <- gsub("other _ character", "other + character", disparity)
disparity <- gsub("range \\+variance", "range \\+ variance", disparity)
disparity <- gsub("geometric ", "", disparity)

@@

## Clean the matchings
tests <- gsub("distance Plinear", "linear", tests)
tests <- gsub("multivariate t_test \\(Hotellings' T\\^2 test\\)", "t_test", tests)
tests <- gsub("Kruskal-Wallis", "anova", tests)
tests <- gsub("distance Pregressions", "regressions", tests)

>>>>

## Clean the matchings
disparity <- gsub("ss", "s", gsub("ss", "s", disparity))
disparity <- gsub(" and ", " \\+ ", disparity)
disparity <- gsub("DTT pair_distances", "pair_distances", disparity)
disparity <- gsub("DTT pair_distances", "pair_distances", disparity)
disparity <- gsub("range variance", "range \\+ variance", disparity)
disparity <- gsub("distances from centre", "centroids", disparity)
disparity <- gsub("distances from centroids", "centroids", disparity)
disparity <- gsub("distances to centroids", "centroids", disparity)
disparity <- gsub("mean ", "", disparity)
disparity <- gsub("median ", "", disparity)
disparity <- gsub("average ", "", disparity)
disparity <- gsub("other _ character", "other + character", disparity)
disparity <- gsub("range \\+variance", "range \\+ variance", disparity)
disparity <- gsub("geometric ", "", disparity)
disparity <- gsub("ranges", "range", disparity)
disparity <- gsub("DTT pairwise squared distances", "pair_distances", disparity)

@@

## Clean the matchings
tests <- gsub("distance Plinear", "linear", tests)
tests <- gsub("multivariate t_test \\(Hotellings' T\\^2 test\\)", "t_test", tests)
tests <- gsub("Kruskal-Wallis", "anova", tests)
tests <- gsub("distance Pregressions", "regressions", tests)
tests <- gsub("Non-regressions", "regressions", tests)
